%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Working Experiences}

% \vspace{-0.1cm}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Backend Software Engineer} % Role
    {ByteDance} % Event
    {Beijing, China} % Location
    {Sep. 2017 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} 
        \item {Facilitated the developing iteration of our product, "Xigua Video", a cross-platform video application. Designed and implemented the technical solutions for requirements as the core developer and tech leader.}  
        \item {Took charge of maintaining the core back-end micro-services, which serves \textbf{50 million} daily active users. Contributed to improving the availability and performance of the core service. The core service is able to response to \textbf{100K QPS} during peak hours and the SLA of service reaches \textbf{99.99\%}}
        % \item {Constantly refactored legacy systems with \textbf{Golang} to improve utilization of the CPU and memory resource and reduce human maintaining costs.}
        \item {Generated online product metrics and exported data to offline data warehouses using \textbf{Kafka}, Utilized \textbf{Hive} and \textbf{SparkSQL} to analyze AB Test data to exploit product potentials.}
      \end{cvitems}
    }
    %\vspace{-0.5cm}
%---------------------------------------------------------

  \cventry
    {Big Data Software Engineer} % Job title
    {Sohu.com} % Organization
    {Beijing, China} % Location
    {Aug. 2015 - Sep. 2017} % Date(s)
    {
        \begin{cvitems}
          \item{Optimized the workflows of the advertisement Click-Through-Rate model training process by setting up \textbf{Azkaban}. Improved the efficiency of different machine learning algorithms(LR and GBDT) to reduce the cost of CPU and memory resources.}
          \item{Restructured the ETL(Extract-Transform-Load) process with \textbf{Spark-Streaming} and implemented a web portal to visualize user action data.}
          \item{Implemented a personalized recommendation system with \textbf{Spring Framework}. Built the corresponding monitor system with \textbf{Redis} and \textbf{HBase}.}
        \end{cvitems}
    }
    
%---------------------------------------------------------
% \vspace{-0.05cm}
  \cventry
    {Member of Technical Stuff Intern} % Job title
    {VMware} % Organization
    {Beijing, China} % Location
    {Nov. 2012 - May 2013} % Date(s)
    {
      \begin{cvitems}
        \item {Implemented script tools to simplify the deployment process of \textbf{Cloud Foundry}, an open-source PaaS platform.}
        \item {Implemented a web-based application migration platform with \textbf{Ruby on Rails}}
      \end{cvitems}
    }
    % \vspace{-0.5cm}

%---------------------------------------------------------
\end{cventries}
