%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Major Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventrynew
    {Related Tech:Golang, RPC, MySQL, Redis, Nginx, Docker, CI/CD} % related tech
    {Launched A Cross-Platform Video APP} % Event
    {ByteDance} % Location
    {Sep. 2017 - July. 2019}
    {
      \begin{cvitems} 
        \item {Designed and implemented backend microservices to serve the basic scenario of watching videos.} %Daily active users increased from 0 to \textbf{50000+} within the first 3 months after deploying online.}
        \item {Develped the content management system from ground up, enriching the video contents that users consume.}
        \item {Built the private networking architecture with external content partner, ensuring the security of content.} %Made it launched by actively negotiating it with the network operators.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventrynew
    {Related Tech: Golang, Mysql, Redis, Python, A/B Test} % Job title
    {Optimized Legacy Systems Performance} % Organization
    {ByteDance} % Location
    {Oct. 2017 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} 
        \item {Refactored API gateway module by changing \textbf{python} into \textbf{Golang} implementation, reducing \textbf{80\%} server resource cost.}
        \item {Refactored user interaction module, adding local cache and sharding DB instances by which the throughput increased by \textbf{400\%}.}
        \item {Leveraged unit tests, CI and CD to avoid unexpected defects introduced by refactoring.}
      \end{cvitems}
    }

 %---------------------------------------------------------

  \cventrynew
    {Related Tech: Azkaban, Java, Haddop, Spark} % Job title
    {Optimized Advertisement CTR model training workflow} % Organization
    {Sohu.com} % Location
    {Jan. 2016 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimized the offline workflow of training advertisement CRT models by parallelizing independent Hadoop batch training steps, reducing about \textbf{35\% running time.}}
        \item {Expedited online streaming workflow with \textbf{Spark-Streaming} and made it in compliance with different machine learning algorithms.}
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------

  \cventrynew
    {Related Tech: JVM, Spring Framework, Zookeeper, CI} % Job title
    {Developed a personalized recommendation engine} % Organization
    {Sohu.com} % Location
    {May. 2016 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed the architecture of the system and built the first online version from ground up.}
        \item {Set up continuous integration environment, reducing the deploying cost.}
        \item {Tuned JVM parameters to optimize the performance. Increased instance throughput by \textbf{20\%}.}
      \end{cvitems}
    } 
\end{cventries}
